---
title: Analysis Result
author: ''
date: '2021-11-16'
slug: analysis-result
categories: []
tags: []
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(plotly)

```
# Analysis on Lending data of Australia

### Background

Based on data disclosed by [Australia Bureau of Statistics](https://www.abs.gov.au/AUSSTATS/abs@.nsf/Lookup/5601.0Main+Features1Dec%202018?OpenDocument=), in 2018, lending to household has reached a lowest point since 2015 and lending to commercial kept on fluctuating during 2015 to 2018.

Lending to household, or lending to individual provides a general estimation on citizen's willingness on consumption. With a sharp decrease on household lending, there should be a clear trend on national consumption willingness.

On the other hand, lending to commercial provides a view on the macro economics.

In this analysis, we try to understand the trend of lending volume in 2018 to generate some insignt on the macro economics.

### Data Preparation

Data source of this analysis comes from [Australia Bureau of Statistics](https://stat.data.abs.gov.au//Index.aspx?QueryId=386). This contains the value of commitment of 59 types of Loan Purpose under 4 main Categories are contained. Below table\@ref(tab:head) shows a partial list of the loan purpose.

```{r head, echo=FALSE, message=FALSE, warning=FALSE}
purpose= read.csv("LENDING.csv")

cate = data.frame(unique(purpose[c("Finance.Type","Purpose")]))

attach(cate)

knitr::kable(head(cate[order(Purpose),],5), caption = "Loan Purpose")

```
Usually, lending is splitting into personal loan and commercial loan. In this case, we use a pie chart to see the distribution of each of the loan types. From the below chart\@ref(fig:type), we can clearly see that, Commercial Financing and Personal Financing took up most of percentile. This supports the assumption we have at the beginning of this section.
```{r type, echo=FALSE, fig.cap='Distribution of Financing Purpose', tidy=FALSE}

type = purpose %>% 
  group_by(Finance.Type)%>%
  summarise(total_commitement = sum(Value, na.rm = TRUE))

p<-ggplot(data=type, aes(x="", y=total_commitement,fill = Finance.Type)) +
  geom_bar(width = 1,stat="identity")+ 
  coord_polar("y", start=0)+ 
  scale_fill_brewer(palette="Blues")+
  theme_minimal()
p

```
### General Understanding

Although we have a general view that Personal loan kept on decreasing since 2015, while Commercial Financing is fluctuating, we need a deeper understanding on how loan commitment behaved in 2018. Here we first generate a line chart for the total commitment\@ref(fig:smooth), and followed with a combine line chart of separate types of loans\@ref(fig:two).

```{r smooth, echo=FALSE, fig.cap='Total value of commitments trend and Regression Plot', message=FALSE, warning=FALSE, tidy=FALSE}
total = purpose %>% 
  group_by(TIME)%>%
  summarise(total_commitement = sum(Value, na.rm = TRUE))

y_m = separate(data = total, col = TIME, into = c("Year", "Month"), sep = "-")

y_m$Month = as.integer(y_m$Month)

p<-ggplot(data=y_m, aes(x=Month, y=total_commitement)) +
  geom_point(shape = 1)  +
  geom_smooth(method = lm)
p

```

```{r two, echo=FALSE, fig.cap='Commercial and Personal Loan Trend', message=FALSE, warning=FALSE, tidy=FALSE}

total_type = purpose %>% 
  group_by(TIME,Finance.Type)%>%
  summarise(total_commitement = sum(Value, na.rm = TRUE))

total_type = separate(data = total_type, col = TIME, into = c("Year", "Month"), sep = "-")

total_type$Month = as.integer(total_type$Month)

total_type = total_type%>%
  filter(Finance.Type=='Commercial Finance'|Finance.Type=='Personal Finance')

p<-ggplot(data=total_type, aes(x=Month, y=total_commitement)) +
  geom_line(aes(color = Finance.Type, linetype = Finance.Type)) + 
  scale_color_manual(values = c("darkred", "steelblue"))
p

```

As a result, we can still clearly see the trend. For personal loan, the value keep on decreasing during the 11 months, while commercial loan increase and fluctuating.

### Relationship with Economic Estimators

The main purpose of this analysis is to understand the relationship between loan commitment and some economic estimators.

As Australia government only disclosed [CPI (Consumer Price Inflation)](https://www.abs.gov.au/statistics/economy/price-indexes-and-inflation/consumer-price-index-australia/sep-2021) estimator every three months, it would not be easy to compare CPI with personal loan commitment in one plot.

From graph below\@ref(fig:cpi), we can see a significant decline during 2018, which fits the decrease of Personal Loan commitment.

```{r cpi, echo=FALSE, fig.cap='CPI Trend from 2014 to 2021', message=FALSE, warning=FALSE, tidy=FALSE}

cpi = read.csv("CPI.csv")
colnames(cpi)[1]<-c("Month")
p<-ggplot(data=cpi, aes(x=Month, y=CPI,group = 1)) +
  geom_line(linetype = "dashed")+
  geom_point() + 
  theme(axis.text.x = element_text(size=10, angle=45))
p

```

### Conclusion

In conclusion, personal loan commitment is a way to reflect the Consumer Price Inflaction. These two estimators are highly correlated and shows the trend of citizen consumption level.