---
title: Visualization using ggplot
author: 'Qiyuan Yang'
date: '2021-11-13'

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
purpose= read.csv("LENDING.csv")

```

This dataset contains information of the value of commitments of each type of loan purpose from January 2018 to November 2018. 

<!--more-->

Here we try to show a total trend of the value of commitments.\@ref(fig:total)

```{r total, echo=FALSE, fig.cap='Total value of commitments trend', tidy=FALSE}

total = purpose %>% 
  group_by(TIME)%>%
  summarise(total_commitement = sum(Value, na.rm = TRUE))

p<-ggplot(data=total, aes(x=TIME, y=total_commitement)) +
  geom_point(shape = 1)  
p

```
We can see a clear growth trend on the total financing commitment, so we can do a smoothing with this dataset. Before this, we need a transform of the current data table as the **TIME** feature here is not a variable that can us to fit the *geom_smooth* function.

```{r smooth, echo=FALSE, fig.cap='Total value of commitments trend and Regression Plot', message=FALSE, warning=FALSE, tidy=FALSE}

y_m = separate(data = total, col = TIME, into = c("Year", "Month"), sep = "-")

y_m$Month = as.integer(y_m$Month)

p<-ggplot(data=y_m, aes(x=Month, y=total_commitement)) +
  geom_point(shape = 1)  +
  geom_smooth(method = lm)
p

```

There is a **significant** growing trend in the plot above\@ref(fig:smooth), and with a 95% confidence band the gray area covers most of the points. However, we can see that some of the points are higher than the expected value, and there seems like a seasonal trend for these points. **3rd, 6th months** are higher than other months, and there is also a growing trend after September. In this case we can guess that the total commitement may have seasonal behaviour, and we can test it if we have more data.


But each type of financing purpose actually make difference. 

We can see from the pie chart below,\@ref(fig:type) Commercial Financing and Personal Financing took up most of the Financing commitment while the remaining two financing purpose even not taking up to 1%.

```{r type, echo=FALSE, fig.cap='Distribution of Financing Purpose', tidy=FALSE}

type = purpose %>% 
  group_by(Finance.Type)%>%
  summarise(total_commitement = sum(Value, na.rm = TRUE))

p<-ggplot(data=type, aes(x="", y=total_commitement,fill = Finance.Type)) +
  geom_bar(width = 1,stat="identity")+ 
  coord_polar("y", start=0)+ 
  scale_fill_brewer(palette="Blues")+
  theme_minimal()
p

```

